---
title: "Data Products Week 3 Assignment"
author: "Jared Brooks"
date: "3/5/2018"
output: ioslides_presentation
---

<style type="text/css">

h3 {
   font-size: 20px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Poisson Histogram

### Here we are simply plotting histograms of Poisson distributions with varying values of lambda toggled with the slider. We see that as the value of lambda increases, the distribution looks more normal.

```{r}
suppressMessages(library(plotly))
#x <- rnorm(5000)
# create data
aval <- list()
for(step in 1:20){
  aval[[step]] <-list(visible = FALSE,
                      name = paste0('lambda = ', step),
                      x=rpois(2000, step),
                      y=rpois(2000, step))
}
```

```{r}
aval[1][[1]]$visible = TRUE
steps <- list()
p <- plot_ly()
for (i in 1:20) {
  
  
  #p <- plot_ly(x = aval[i][[1]]$x, y = aval[i][[1]]$y, visible = aval[i][[1]]$visible,
  #             name = aval[i][[1]]$name, hoverinfo = 'name') %>% 
  #p <- plot_ly()
  #p <- add_histogram2dcontour(p, x = aval[i][[1]]$x, y = aval[i][[1]]$y, 
  #                            visible = aval[i][[1]]$visible, name = aval[i][[1]]$name, 
  #                            hoverinfo = 'name', showscale=FALSE, ncontours=20, 
  #                            colorscale='hot', contours = list(coloring='heatmap')) #%>%
      #add_markers(x = aval[i][[1]]$x[1:500], y = aval[i][[1]]$y[1:500], marker=list(size=2),
      #              color=I("black"), opacity=.5) #%>%
  #p <- layout(p, xaxis=list(showgrid=FALSE, zeroline=FALSE), 
  #             yaxis=list(showgrid=FALSE, zeroline=FALSE),
  #             showlegend=FALSE)
  p <- add_histogram(p, x = aval[i][[1]]$x,
                     visible = aval[i][[1]]$visible, name = aval[i][[1]]$name)
                     #hoverinfo = 'name') #%>%
    #add_histogram(x = aval[i][[1]]$y,
    #                 visible = aval[i][[1]]$visible, name = aval[i][[1]]$name,
    #                 hoverinfo = 'name', color=I('blue')) %>%
    #layout(barmode="overlay")
  step <- list(args = list('visible', rep(FALSE, length(aval))),
               method = 'restyle')
  step$args[[2]][i] = TRUE  
  steps[[i]] = step 
}
```

```{r}
p <- p %>%
  layout(sliders = list(list(active = 0,
                             currentvalue = list(prefix = "Frequency: "),
                             steps = steps)))
```

```{r}
p
```

## 2D Poisson Histogram

### Here we see a 2D Possion histogram where the x and y values are both Poisson distributions of the same size and lambda, plotted with a zsmooth function.

```{r}
aval[1][[1]]$visible = TRUE
steps <- list()
p <- plot_ly()
for (i in 1:20) {
  
  
  #p <- plot_ly(x = aval[i][[1]]$x, y = aval[i][[1]]$y, visible = aval[i][[1]]$visible,
  #             name = aval[i][[1]]$name, hoverinfo = 'name') %>% 
  #p <- plot_ly()
  #p <- add_histogram2dcontour(p, x = aval[i][[1]]$x, y = aval[i][[1]]$y, 
  #                            visible = aval[i][[1]]$visible, name = aval[i][[1]]$name, 
  #                            hoverinfo = 'name', showscale=FALSE, ncontours=20, 
  #                            colorscale='hot', contours = list(coloring='heatmap')) #%>%
      #add_markers(x = aval[i][[1]]$x[1:500], y = aval[i][[1]]$y[1:500], marker=list(size=2),
      #              color=I("black"), opacity=.5) #%>%
  #p <- layout(p, xaxis=list(showgrid=FALSE, zeroline=FALSE), 
  #             yaxis=list(showgrid=FALSE, zeroline=FALSE),
  #             showlegend=FALSE)
  p <- add_histogram2d(p, x = aval[i][[1]]$x, y = aval[i][[1]]$y, zsmooth='best',
                     visible = aval[i][[1]]$visible, name = aval[i][[1]]$name, showscale = FALSE)
                     #hoverinfo = 'name') #%>%
    #add_histogram(x = aval[i][[1]]$y,
    #                 visible = aval[i][[1]]$visible, name = aval[i][[1]]$name,
    #                 hoverinfo = 'name', color=I('blue')) %>%
    #layout(barmode="overlay")
  step <- list(args = list('visible', rep(FALSE, length(aval))),
               method = 'restyle')
  step$args[[2]][i] = TRUE  
  steps[[i]] = step 
}
```

```{r}
p <- p %>%
  layout(sliders = list(list(active = 0,
                             currentvalue = list(prefix = "Frequency: "),
                             steps = steps)))
```

```{r}
p
```



